---
title: "FinalModels-ICPhS"
author: "Tom Offrede"
date: "2022-12-09"
output:
  html_document:
    toc: true
    toc_float: 
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(lmerTest)
library(ggdist)
library(mediation)

`%!in%` <- Negate(`%in%`)

folder <- "C:/Users/offredet/Documents/1HU/ExperimentEyes/Data/All/"
folderConvPlots <- "C:/Users/offredet/Documents/1HU/ExperimentEyes/Data/ConvergencePlots/"
files <- list.files(folder, "RData")
fileBase <- files[grepl("Baseline", files)]
fileConv <- files[grepl("Conversation", files) & !grepl("Including", files)]

load(paste0(folder, "dataBaseline.RData"))
load(paste0(folder, "dataConversation.RData"))

dac <- dac[!grepl("Impairment|Dyslexia|Gender|Education|Age", names(dac))]

dac <- dac %>%
  filter(!grepl("Robot", speaker)) %>% 
  mutate_at(c("turnDur", "turn", "f0mean", "f0sd", "intensMean", "intensMax", "robPrevf0mean", "robPrevf0meanMock", "gapDur", "intimMean", "intimSD", "intimMed", "IPUDur", "robPrevf0sd", "robPrevf0sdMock", "robPrevIntMean", "robPrevIntMeanMock", "robPrevIntMax", "robPrevIntMaxMock"), as.numeric) %>%
  mutate_at(c("speaker", "condition", "Order", "task"), as.factor) %>% 
  group_by(speaker) %>%
  mutate(turnDurNormal = (turnDur - min(turnDur, na.rm = TRUE)) / (max(turnDur, na.rm = TRUE) - min(turnDur, na.rm = TRUE)),
         turnDurc = turnDur - mean(turnDur, na.rm=TRUE),
         robf0meanc = robPrevf0mean - mean(robPrevf0mean, na.rm=TRUE),
         robf0sdc = robPrevf0sd - mean(robPrevf0sd, na.rm=TRUE),
         robIntMeanc = robPrevIntMean - mean(robPrevIntMean, na.rm=TRUE),
         robIntMaxc = robPrevIntMax - mean(robPrevIntMax, na.rm=TRUE),
         intimc = intimMean - mean(intimMean, na.rm=TRUE),
         intensMeanC = intensMean - mean(intensMean, na.rm=TRUE),
         intensMaxC = intensMax - mean(intensMax, na.rm=TRUE),
         f0CV = f0sd / f0mean,
         robf0CV = robPrevf0sd / robPrevf0mean,
         robf0CVc = robf0CV - mean(robf0CV, na.rm=TRUE),
         mockf0meanC = robPrevf0meanMock - mean(robPrevf0meanMock, na.rm=TRUE),
         mockf0sdC = robPrevf0sdMock - mean(robPrevf0sdMock, na.rm=TRUE),
         mockf0CV = robPrevf0sdMock / robPrevf0meanMock,
         mockf0CVc = mockf0CV - mean(mockf0CV, na.rm=TRUE),
         f0sdZ = (f0sd - mean(f0sd, na.rm=TRUE))/sd(f0sd, na.rm=TRUE),
         robf0sdZ = robf0sdc / sd(robPrevf0sd, na.rm=TRUE),
         f0CVz = (f0CV - mean(f0CV, na.rm=TRUE))/sd(f0CV, na.rm=TRUE),
         robf0CVz = robf0CVc / sd(robf0CV, na.rm=TRUE),
         f0meanZ = (f0mean - mean(f0mean, na.rm=TRUE))/sd(f0mean, na.rm=TRUE),
         robf0meanZ = robf0meanc / sd(robPrevf0mean, na.rm = TRUE),
         f0meanc = (f0mean - mean(f0mean, na.rm=TRUE)/sd(f0mean, na.rm=TRUE)),
         f0sdc = (f0sd - mean(f0sd, na.rm=TRUE)/sd(f0sd, na.rm=TRUE))) %>%
  ungroup() %>% 
  mutate(ESc = EmotionalStability - mean(EmotionalStability, na.rm=TRUE),
         Agreec = Agreeableness - mean(Agreeableness, na.rm=TRUE),
         Conscc = Conscientiousness - mean(Conscientiousness, na.rm=TRUE),
         Extrac = Extraversion - mean(Extraversion, na.rm=TRUE),
         IOc = IntellectOpenness - mean(IntellectOpenness, na.rm=TRUE),
         ConvQualc = PCConvQuality - mean(PCConvQuality, na.rm=TRUE),
         EvalRobotc = PCEvalRobot - mean(PCEvalRobot, na.=TRUE),
         IPUDurC = IPUDur - mean(IPUDur, na.rm=TRUE)) #%>% 
  # filter(scoreEN > 60) # see with and without low-level participants


dab <- dab %>%
  mutate_at(c("condition"), as.factor) %>% 
  group_by(speaker) %>% 
  mutate(robf0meanc = robPrevf0mean - mean(robPrevf0mean, na.rm=TRUE),
         robf0sdc = robPrevf0sd - mean(robPrevf0sd, na.rm=TRUE),
         mockf0meanC = robPrevf0meanMock - mean(robPrevf0meanMock, na.rm=TRUE),
         mockf0sdC = robPrevf0sdMock - mean(robPrevf0sdMock, na.rm=TRUE)) %>% 
  ungroup()
```

# Robot's effect on convergence

## f0 mean

```{r}
ggplot(dac, aes(robPrevf0mean, f0mean))+
  theme_minimal()+
  geom_point()+
  geom_smooth()+
  labs(title="Robot's F0's Influence on Human's F0",
       y="Human's F0 mean",
       x="Robot's F0 mean")+
  theme(title = element_text(size=18))+
  ylim(70,205)+
  xlim(74, 200)
# ggsave(paste0(folder, "RobotHumanF0.png"), units = "px")
```

```{r}
ggplot(dac, aes(robPrevf0mean, f0mean))+
  theme_minimal()+
  geom_point()+
  geom_smooth(method="lm")+
  labs(title="Robot's F0's Influence on Human's F0",
       y="Human's F0 mean",
       x="Robot's F0 mean")+
  theme(title = element_text(size=18))+
  ylim(70,205)+
  xlim(74, 200)+
  facet_wrap(~speaker)
# ggsave(paste0(folder, "RobotHumanF0-Individual.png"), units = "px", width=3500, height=2159)
```

There is a general effect of synchrony to the robots. There might also be a *condition* effect: people only converge to the robot in the *Gaze Aversion* condition, but the AIC of the models suggests that the model without *condition* is better. There might also be a *convergence* effect: adding "turn" as an interacting predictor also gives a significant model, but, again, AIC comparison suggests the simpler model is better.

```{r}
summary(f1 <- lmer(f0mean ~ robf0meanc + (1 | speaker), dac))

summary(f2 <- lmer(f0mean ~ robf0meanc : condition + (1 | speaker), dac)) # no random slopes so that this model is comparable with the one above
anova(f1, f2)

summary(f3 <- lmer(f0mean ~ robf0meanc : turn + (1 | speaker), dac))
anova(f1, f3)

par(mfrow=c(2,2))
hist(resid(f1))
qqnorm(resid(f1));qqline(resid(f1))
plot(fitted(f1), resid(f1))
```

### R^2^ (marginal and conditional)

```{r}
MuMIn::r.squaredGLMM(f1)
```

## f0 mean plots

```{r}
# dat <- dac %>%
#   group_by(speaker, condition) %>% 
#   mutate(IPUoverall = 1:n()) %>% 
#   ungroup() %>% 
#   select(speaker, turn, IPUoverall, f0mean, robPrevf0mean, condition)
# 
# for(s in unique(dac$speaker)){
#   for(c in unique(dac$condition)){
#     if(c=="NG"){cond = "Fixed Gaze"}else{cond = "Gaze Aversion"}
#     d <- dat %>%
#       filter(speaker==s, condition==c)
#     dR <- d %>%
#       select(-f0mean) %>% 
#       rename(f0mean = robPrevf0mean) %>% 
#       mutate(speaker = "Robot")
#     d$robPrevf0mean <- NULL
#     d <- rbind(d, dR)
#     ggplot(d, aes(IPUoverall, f0mean, color=speaker))+
#       geom_point()+
#       geom_smooth(method="loess")+
#       ggtitle(paste0(s, " - ", cond))
#     ggsave(paste0(folderConvPlots, c, "-", s, ".png"))
#   }
# }
# 
# # for paper: NG-MDE (convergence/synchrony), GA-FQD (divergence), NG-JBY (conv then div)
# 
# for(s in c("MDE", "JBY", "FQD")){
#   if(s!="FQD"){
#     d <- dat %>%
#       filter(speaker==s, condition=="NG")
#   }
#   if(s=="FQD"){
#     d <- dat %>%
#       filter(speaker==s, condition=="GA")
#   }
#     dR <- d %>%
#       select(-f0mean) %>% 
#       rename(f0mean = robPrevf0mean) %>% 
#       mutate(speaker = "Robot")
#     d$robPrevf0mean <- NULL
#     d <- rbind(d, dR)
#     if(s=="MDE"){
#       m <- ggplot(d, aes(IPUoverall, f0mean, color=speaker))+
#         theme_classic()+
#         geom_point()+
#         geom_smooth(method="loess")+
#         scale_color_grey(labels=c("Human", "Robot"))+
#         labs(title="A",
#              color="Speaker",
#              y="F0 mean",
#              x="Time")+
#         theme(axis.text.x=element_blank(),
#               axis.ticks.y = element_blank(),
#               axis.ticks.x = element_blank())+
#         ylim(100,200)
#     }
#     if(s=="JBY"){
#       j <- ggplot(d, aes(IPUoverall, f0mean, color=speaker))+
#         theme_classic()+
#         geom_point()+
#         geom_smooth(method="loess")+
#         scale_color_grey(labels=c("Human", "Robot"))+
#         labs(title="C",
#              color="Speaker",
#              y="F0 mean",
#              x="Time")+
#         theme(axis.text.x=element_blank(),
#               axis.ticks.y = element_blank(),
#               axis.ticks.x = element_blank())+
#         ylim(100,200)
#     }
#     if(s=="FQD"){
#       f <- ggplot(d, aes(IPUoverall, f0mean, color=speaker))+
#         theme_classic()+
#         geom_point()+
#         geom_smooth(method="loess")+
#         scale_color_grey(labels=c("Human", "Robot"))+
#         labs(title="B",
#              color="Speaker",
#              y="F0 mean",
#              x="Time")+
#         theme(axis.text.x=element_blank(),
#               axis.ticks.y = element_blank(),
#               axis.ticks.x = element_blank())+
#         ylim(100,200)
#     }
#   }
# }
# 
# arr <- ggarrange(m, f, j, ncol=1)
# fig <- annotate_figure(arr, top = text_grob("Examples of F0 mean patterns", size=16))
# 
# ggsave(paste0(folder, "icphs.png"), plot=fig, height=2000, width=1500, units = "px")

```

# Calculate number of IPUs per turn -- just to check

```{r}
IPUno <- dac %>% 
  dplyr::select(speaker, condition, turn) %>% 
  group_by(speaker, condition, turn) %>% 
  mutate(numberIPUs = n()) %>% 
  ungroup() %>% 
  distinct()
table(IPUno$numberIPUs)
names(dac)
```

### Intimacy

#### Convergence

```{r}
summary(f1i <- lmer(f0mean ~ robf0meanc : intimc + (1 | speaker), dac))
```

#### f0 mean

intimacy reduces f0 mean and robot (condition nor robot'S f0) doesnt affect this effect. Intensity is not affected by intimacy.

```{r}
summary(f1 <- lmer(f0mean ~ intimc + (1  | speaker), dac))
summary(f2 <- lmer(f0mean ~ intimc : condition + (1  | speaker), dac))
anova(f1, f2)

par(mfrow=c(2,2))
hist(resid(f1))
qqnorm(resid(f1));qqline(resid(f1))
plot(fitted(f1), resid(f1))
```

#### Intensity

```{r}
summary(i <- lmer(intensMean ~ intimc + (1 | speaker), dac))

par(mfrow=c(2,2))
hist(resid(i))
qqnorm(resid(i));qqline(resid(i))
plot(fitted(i), resid(i))
```

##### Mediation analysis (f0 ~ intimacy + intensity)


```{r}
ggplot(dac, aes(intimMean, f0mean))+
  theme_minimal()+
  geom_point()+
  geom_smooth(method="lm")+
  labs(title="Intimacy and F0",
       y="F0 mean",
       x="Intimacy Ratings")+
  theme(title = element_text(size=18))
ggsave(filename = paste0(folder, "intimacy-f0.png"), units = "px")
```


*(see tutorial here: https://towardsdatascience.com/doing-and-reporting-your-first-mediation-analysis-in-r-2fe423b92171)*

Intimacy does seem to affect f0 directly, independently of intensity.

```{r}
summary(fit.totalEffect <- lme4::lmer(f0mean ~ intimc + (1|speaker), dac))
summary(fit.mediator <- lme4::lmer(intensMean ~ intimc + (1|speaker), dac))
summary(fit.both <- lme4::lmer(f0mean ~ intimc + intensMeanC + (1|speaker), dac))

medResult <- mediate(fit.mediator, fit.both, treat = "intimc", mediator = "intensMeanC", boot=F)
summary(medResult)
```


# Questionnaire ratings

### Means and SDs
```{r}
dat <- dac %>%
  mutate(g = paste0(speaker, condition)) %>% 
  filter(!grepl("Robot", speaker), !duplicated(g))

# Conversational Quality, Fixed Gaze condition
mean(dat$PCConvQuality[dat$condition=="NG"]) # mean: 6.97
sd(dat$PCConvQuality[dat$condition=="NG"]) # SD: 1.24

# Conversational Quality, Gaze Aversion condition
mean(dat$PCConvQuality[dat$condition=="GA"]) # mean: 6.99
sd(dat$PCConvQuality[dat$condition=="GA"]) # SD: 1.1

# Evaluation of Robot, Fixed Gaze condition
mean(dat$PCEvalRobot[dat$condition=="NG"]) # mean: 6.5
sd(dat$PCEvalRobot[dat$condition=="NG"]) # SD: 1.3

# Evaluation of Robot, Gaze Aversion condition
mean(dat$PCEvalRobot[dat$condition=="GA"]) # mean: 6.25
sd(dat$PCEvalRobot[dat$condition=="GA"]) # SD: 1.09


##################################


# Conversational Quality, Fixed Gaze condition
mean(dac$PCConvQuality[dac$condition=="NG"]) # mean: 7.11
sd(dac$PCConvQuality[dac$condition=="NG"]) # SD: 1.21

# Conversational Quality, Gaze Aversion condition
mean(dac$PCConvQuality[dac$condition=="GA"]) # mean: 7.01
sd(dac$PCConvQuality[dac$condition=="GA"]) # SD: 1.05

# Evaluation of Robot, Fixed Gaze condition
mean(dac$PCEvalRobot[dac$condition=="NG"]) # mean: 6.54
sd(dac$PCEvalRobot[dac$condition=="NG"]) # SD: 1.39

# Evaluation of Robot, Gaze Aversion condition
mean(dac$PCEvalRobot[dac$condition=="GA"]) # mean: 6.27
sd(dac$PCEvalRobot[dac$condition=="GA"]) # SD: 1.07

```


```{r}
ggplot(dat, aes(condition, PCConvQuality))+
  theme_minimal()+
  stat_halfeye(adjust = .5,  width = .5, justification = -.2, .width = c(.5, .95), fill="#9bafbd")+
  geom_boxplot(width=.13, notch = TRUE)+
  scale_x_discrete(labels=c("Gaze Aversion", "Fixed Gaze"))+
  labs(title="Conversational Quality",
       x="",
       y="Ratings")
# ggsave(paste0(folder, "convQual.png"))

summary(cq1 <- lmer(PCConvQuality ~ condition + (1 |speaker), dat))

par(mfrow=c(2,2))
plot(fitted(cq1), resid(cq1))
hist(resid(cq1))
qqnorm(resid(cq1));qqline(resid(cq1))
```


```{r}
ggplot(dat, aes(condition, PCEvalRobot))+
  theme_minimal()+
  stat_halfeye(adjust = .5,  width = .5, justification = -.2, .width = c(.5, .95), fill="#9bafbd")+
  geom_boxplot(width=.13, notch = TRUE)+
  scale_x_discrete(labels=c("Gaze Aversion", "Fixed Gaze"))+
  labs(title="Evaluation of Robot",
       x="",
       y="Ratings")
# ggsave(paste0(folder, "evalRobot.png"))

summary(rq1 <- lmer(PCEvalRobot ~ condition + (1|speaker), dat))

par(mfrow=c(2,2))
plot(fitted(rq1), resid(rq1))
hist(resid(rq1))
qqnorm(resid(rq1));qqline(resid(rq1))
```

# Session Info

```{r}
sessionInfo()
```

